AttCRISPR : an spacetime interpretable model for sgRNA efficiency prediction

### 2020-10-28 Paper/main.tex
10-26 paper&attention code
10-28 paper

 Specifically, we use a vector $A_i$ to build the first-order original preference at position $i$ within sgRNA sequence, then
 define $\tilde{A}$ as the first-order combine preference matrix (or just first-order preference), which means $\tilde{A}$ can be expressed linearly by $A$ as follow
\begin{equation}
\tilde{A}=BA\label{eq:04}
\end{equation}
where the weight matrix $B\in\mathbb{R}^{l\times l}$ is learned through attention mechanism. 
Then the predicted value can be expressed as
\begin{equation}
y=\sum_i^lW_i\tilde{A}_i\cdot {X_e}_i\label{eq:05}
\end{equation}
 where $W\in\mathbb{R}^l$ denotes a non-negative weight vector, $W_i$ denotes the weight of the $i$-th position, ${X_e}_i$ denotes the embedding vector of the nucleotide at $i$-th position.
 Assume that in Equation~(\ref{eq:04}) the first-order original preference at each position is relatively independent and weight matrix $B$ is independent of any first-order original preference, 
 then the total differential of the first-order preference at $i$-th position $\tilde{A}_i$ could be written as
\begin{equation}
d\tilde{A}_i=\sum_j^lB_{ij}EdA_j\label{eq:07}
\end{equation}
where $E$ is the identity matrix, and we call $B$ as the second-order preference matrix, 
it can explain how a particular pattern containing two nucleotides affects the base sequence, 
for example, how does the degree of preference for the G adjacent to PAM be affected by a T at 2 bases upstream?

@@

>>>>

 Specifically, we use a vector $A_i$ to build the first-order original preference at position $i$ within sgRNA sequence, then
 define $\tilde{A}$ as the first-order combine preference matrix (or just first-order preference), which means $\tilde{A}$ can be expressed linearly by $A$ as follow
\begin{equation}
\tilde{A}=BA\label{eq:04}
\end{equation}
where the weight matrix $B\in\mathbb{R}^{l\times l}$ is learned through attention mechanism. 
Then the predicted value can be expressed as
\begin{equation}
y=W \cdot \tilde{A} {X_e}^{T}\label{eq:05}
\end{equation}
 where $W\in\mathbb{R}^l$ denotes a non-negative weight vector. 
 Assume that in Equation~(\ref{eq:04}) the first-order original preference at each position is relatively independent and weight matrix $B$ is independent of any first-order original preference, 
 then the total differential of the first-order preference at $i$-th position $\tilde{A}_i$ could be written as
\begin{equation}
d\tilde{A}_i=\sum_j^lB_{ij}EdA_j\label{eq:07}
\end{equation}
where $E$ is the identity matrix, and we call $B$ as the second-order preference matrix, 
it can explain how a particular pattern containing two nucleotides affects the base sequence, 
for example, how does the degree of preference for the G adjacent to PAM be affected by a T at 2 bases upstream?

@@

\begin{table}[!tpb]
    \processtable{Three sgRNA and their activity \label{Tab:optimum}} 
    {\begin{tabular}{@{}lll@{}}\toprule
        Index & sgRNA & Activity \\\midrule
        8493 & ACATGACTTTGGATTTCCCCAGG & 0.831\\
        8492 & ACATGACTTTGGATTCCCCCAGG & 0.869\\
        8491 & ACATGACTTTGGACTTCCCCAGG & 0.861\\
        \botrule
    \end{tabular}}\footnotesize\setlength{\parindent}{2em}{
\emph{Index} represents its index in the source data (Supplementary Data 1), 
\emph{Activity} represents its activity reported in WT-SpCas9 dataset. }
\end{table}
\begin{figure}[!tpb]
    \centerline{\includegraphics[width=86mm]{local0.eps}}
    \caption{
The scores of sgRNA with index of 8493 obtained by the temporal AttCRISPR. 
The bar plot reveals the score at each position at local level, while the line of dashes reveals the scores at global level. 
At global level we calculated the scores of all sgRNA, then average the scores at each position to obtain the global level which can be used as base line and is helpful to judge the relative height of the scores. }\label{fig:opt}
\end{figure}
\begin{figure}[!tpb]
    \centerline{\includegraphics[width=86mm]{secondorder.eps}}
    \caption{wait2write}\label{fig:heatmap}
\end{figure}
Text
